Towards End-user Web Scraping For Customization

### 2021-04-09 paper.tex
Remved link to web version from demos section

In this section, we show how end-users can create, extend and repair
adapters for Wildcard via demonstration.{ These demos are best viewed as
videos in the online version of this paper
(\url{https://kapaya.github.io/px21}).}

>>>>

In this section, we show how end-users can create, extend and repair
adapters for Wildcard via demonstration.
